resistanceModelNotesAndy

### 2016-03-02 resistanceModelNotesAndy.Rmd
notes

** 26/8/15 **
submit invoice
from contract : maximum of 25 days at 217 per day

I spent 30.6 days (can claim some against tsetse work, or from future contract ...)

@@

#### can I replace :
Mix1 - Mix_1
Mix2 - Mix_A
Mix3 - Mix_2
"Mixture 1" - "Mix either"
"Mixture 2" - "Mix adaptive"
"Mixture 3" - "Mix both"
done mix2_minus_seq0.25          mixA_minus_seq0.25

>>>>

** 26/8/15 **
submit invoice : from contract : maximum of 25 days at 217 per day
I spent 30.6 days (can claim some against tsetse work, or from future contract ...)

@@

#### replacements done :
Mix1 - Mix_1
Mix2 - Mix_A
Mix3 - Mix_2
"Mixture 1" - "Mix either"
"Mixture 2" - "Mix adaptive"
"Mixture 3" - "Mix both"
done mix2_minus_seq0.25          mixA_minus_seq0.25

done ~ record time spent & when was the last time I claimed on the previous contract ?
Previous contract claimed 15 Sept 2015.
submit invoice : from contract : maximum of 25 days at 217 per day
I spent 30.6 days (can claim some against tsetse work, or from future contract ...)
So time I spent in January on toggl should be on new contract/
To the end of Feb :
Hours		105:45:00
Hours rounded		105.00
Days (/7.5)		14.00
Days remaining (from 85)		71.00

~ can I facet the PRCC mutliplots so I just get one axis ?

~ start creating a proposed slimmed down figs doc (maybe as a word doc using pandoc) proposed for the paper
~~ beware that if I send it to Ian as a doc, he will insert text into it that I may not be able to find.
~~ maybe send it as a pdf first & change to a doc later to allow Ian to copy & paste the figs.
~~ see paper1_results_figs_slimmed.Rmd
